\vspace{-2cm} Kronos \& Krios: Evidence for accretion of rocky planets in a comoving pair of G dwarfs \vspace{-0.5cm}

### 2017-06-25 paper/ms.tex
main text

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair,
    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
    \label{fig:abundances}
  }
\end{figure}

@@

\item [c] Absolute abundances from Myles \etal, in prep.

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2 both similar to the Sun (G2).
In a separate effort to study detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars were obtained using the HIRES spectrograph on the Keck-I
telescope\cite{2016ApJS..225...32B}.
The wavelength coverage is $5164$--$7799$~\AA.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(section~Table~\ref{tab:t1}).

% likely origin given its proximity in phase space
The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
and the 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties,
confirming that they are truly comoving (\ref{supp:dxdv}).
As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
\sunanalog\ are likely a bound wide binary system that formed coevally.

% coevality based on stellar parameters
% TODO reference supplement discussion on age here?
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, \elemH{Si}
in order interpolate the age, mass, and radius of each star
in a grid of Yale-Yonsei model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (see Figure~\ref{fig:yyisofitting}).

% metallicity and abundance difference
However, one of the stars, \bizarreone, is significantly more metal rich than
the other by 0.2~dex in \feh\ ($\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of data and
model between the two stars show significant residuals of almost all metal line
features, largely dominated by \elem{Fe}.
However, for lines of elements that are not as enhanced in \bizarreone\, the
residuals are much smaller in amplitude demonstrating the validity of the
measured abundance differences (Figure~\ref{fig:spec1} and \ref{fig:spec2}).

% novelty
The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K) wide
binary pairs examined using spectra of similar quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (Figure~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
In fact, the abundance pattern of \bizarreone\ is a very unlikely one
for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
implying that a scenario involving Galactic chemical evolution is not plausible
even if we ignore a coeval star, \sunanalog, that we can compare with.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(Figure~\ref{fig:relabun_tcrank}).

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it will be destroyed by proton capture
burning. %TODO: REFERENCE?
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (\figname~\ref{fig:spec2}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

The abundance differences show a strong increasing trend with condensation
temperature ($T_C$) of elements.
In Figure~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\cite{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile in all elements measured.
The difference in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggests a break in $\Tcondens \approx 1200$~K.

We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
planetary material in \bizarreone.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering\cite{} or encounters with a field star\cite{Malmberg:2011aa} can
lead to planet ejection or accretion.
If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
than the other, this may imprint a strong \Tcondens-dependent
abundance differences like those observed in \bizarreone-\sunanalog.

@@

We estimate that accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very close in its properties (\teff, \logg, \feh, age) to the Sun,
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In Figure~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth
composition\cite{2003TrGeo...2..547M} assuming that 2\% of the Sun's mass
is in its convective zone\cite{Pinsonneault:2001aa}.
A volatility trend that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous chondrites
has long been known\cite{mcdonough2001composition}.
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium on the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of Figure~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with $1.6$~dex
enhancement in its \elem{Li}.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep)
approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

What about \sunanalog?
Considering its age of $4.00_{-1.56}^{+1.51}$~Gyr, \sunanalog\ is also enhanced
in \elem{Li} compared to other stars of similar ages by $\approx 1$~dex.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth\ assuming \elem{Li} concentration of $1.1$~ppm
\cite{mcdonough2001composition}.
Unlike \bizarreone, we cannot know the pre-accretion abundances of
\sunanalog.\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider accretion by the Sun.
  In reality, \sunanalog\ may as well have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na and Fe in
\sunanalog.
It is also interesting that \sunanalog\ shows a deficit in the same volatile
and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn}) relative to Fe as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was at least 5 time
smaller than \bizarreone.

What triggered the planet engulfment in the two comoving stars
within the last Gyr remains unclear.
A possibility is that a fly-by interaction with a field star could have
triggered eccentricity excitation of outer planets around each star, which may
have propagated inward through planet-planet scattering, making inner rocky planets
to be accreted\cite{Zakamska:2004aa,Malmberg:2011aa}.
If this is the case, there may be surviving highly eccentric giant planets that are
potentially detectable with future data releases of \gaia.
The two stars have not been included in any publicly released data from planet
search programs.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
  \caption{Expected differences in solar abundances after adding
    varying mass of bulk Earth material.
    Elements are ordered by their $T_C$ on $x$-axis, same as
    Figure~\ref{fig:deltaxh_tcrank}.
    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
    0.03$ respectively.
    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
  }
  \label{fig:vari}
\end{figure}

@@

The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
mass of the star which are difficult quantities to constrain directly through
data.
While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
Figure~\ref{fig:vari}.

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair,
    \bizarreone\ (red circles) and \sunanalog\ (blue squares).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet much less in
    \elem{C}, \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
    \label{fig:abundances}
  }
\end{figure}

@@

\item [c] Absolute abundances from Myles \etal (in prep.).

@@

% general description of the pair and measurements
\sunanalog\ and \bizarreone\ were identified as a candidate comoving star pair
in our recent search for comoving stars using the proper motions and parallaxes
from the {\it Tycho-Gaia Astrometric Solution} catalog (hereafter \tgas), a
component of the first data release of the astrometric space mission \gaia\cite{2016A&A...595A...2G}
(the astrometric measurements are listed in \tablename~\ref{tab:t1}).
The pair has also been previously recognized as a visual double star system
in the Washington Double Star catalog\cite{2001AJ....122.3466M}.
The two stars have spectral types G0 and G2, both similar to the Sun (G2).
In a separate effort to study the detailed chemical abundances of potential
planet-hosting stars, high resolution ($R=\lambda/\Delta\lambda\approx 70000$),
high signal-to-noise ratio (typically $>200$ per pixel in continuum) spectra of
both stars for the wavelength range $5164$--$7799$~\AA were obtained using the
HIRES spectrograph on the Keck-I telescope\cite{2016ApJS..225...32B}.
The resulting measurements include elemental abundances for 15 chemical species
(C, N, O, Na, Mg, Al, Si, Ca, Ti, V, Cr, Mn, Fe, Ni, Y) as well as stellar
parameters and high precision ($\sigma\approx0.2$~\kms) radial velocities
(section~Table~\ref{tab:t1}).

% likely origin given its proximity in phase space
The projected separation between the pair is 1.9 arcmin\ ($\approx 0.01$~pc),
and the maximum-likelihood 3D separation is $\approx 0.6$~pc.
Although selected based only on their astrometry, the two stars
have identical radial velocities within uncertainties,
confirming that they are truly comoving (\ref{supp:dxdv}).
As the separation is smaller than the Jacobi radius (1.2~pc) in the solar
neighborhood for a 2~\msun\ binary system\cite{Jiang:2010aa}, \bizarreone\ and
\sunanalog\ are likely a coeval, bound wide-binary system.

% coevality based on stellar parameters
% TODO reference supplement discussion on age here?
Their stellar parameters also indicate that they are coeval with an age of $\sim 4$~Gyr.
We use the distances (inferred from \gaia\ parallaxes), $V$-band magnitudes,
and $B-V$ colors to obtain bolometric luminosities of the two stars\cite{2003AJ....126..778V}.
We then combine the luminosities with $T_\mathrm{eff}$, \elemH{Fe}, and
\elemH{Si} in order to interpolate the age, mass, and radius of each star
using a grid of (Yale-Yonsei) model isochrones\cite{2013ApJ...776...87S}.
The best-fit isochrone ages of \bizarreone\ and \sunanalog\ are
$4.28_{-1.03}^{+1.11}$~Gyr and $4.00_{-1.56}^{+1.51}$~Gyr, respectively,
consistent with them being coeval (see \figname~\ref{fig:yyisofitting}).

% metallicity and abundance difference
However, one of the stars, \bizarreone, is significantly more metal rich than
the other by 0.2~dex in \feh\ ($\approx 60\%$; \figname~\ref{fig:abundances}).
Moreover, not all elements are equally enhanced: the abundances of \bizarreone\
show selective under-enhancement in \elem{C}, \elem{N}, \elem{O}, \elem{Na},
and \elem{Mn} relative to \elem{Fe} and other refractory elements.
As expected from their measured metallicity difference, the ratio of spectral
data and model between the two stars show significant residuals of almost all
metal line features, largely dominated by \elem{Fe}.
However, for absorption lines of elements that are not as enhanced in
\bizarreone\, the residuals are much smaller in amplitude demonstrating the
validity of the measured abundance differences (\figname~\ref{fig:spec1} and
\ref{fig:spec2}).

% novelty
The observed difference in metallicity and abundances are genuinely rare and
unexpected.
None of the other four twin-like ($\Delta T_\mathrm{eff} \lesssim 100$~K), wide-binary pairs examined using spectra of similar quality and the same
consistent measurement pipeline shows discrepancies in abundances between the
stars at this level\cite{2016ApJS..225...32B} (\figname~\ref{fig:deltaXH}).
The maximum metallicity difference observed in the other pairs is $\Delta\feh =
0.03$~dex with $1\sigma$ statistical uncertainties in \feh\ of $0.01$~dex.
This is consistent with similar studies of metallicity and abundance
differences in wide binaries\cite{Gratton:2001aa,Desidera:2004aa}.
In fact, the abundance pattern of \bizarreone\ is very unusual
for a star that is enhanced in \feh\ by $0.2$~dex relative to \sunanalog\
($\feh\approx 0$; \figname~\ref{fig:deltaXH}),
implying that a scenario involving Galactic chemical evolution is not plausible
even if we ignore the coeval comparison star, \sunanalog.
The difference of $\approx 0.2$~dex is also the largest among a handful of wide
binaries that do show metallicity and abundance differences with varying
significance\cite{Mack:2014aa,Mack:2016aa,Saffe:2015aa,
  Teske:2013aa,Teske:2015aa,Teske:2016aa,Teske:2016ab,Biazzo:2015aa,Ramirez:2015aa}
(\figname~\ref{fig:relabun_tcrank}).

% high Li
Both stars have high surface \elem{Li} abundances considering
their ages of $\sim 4$~Gyr.
The surface lithium abundance in a sun-like star decreases with its age due to
mixing induced by convection or rotation, which brings the lithium into the
interior ($T>2.5 \times 10^{6}$~K) where it is destroyed by proton capture
burning. %TODO: REFERENCE?
The \elem{Li} doublet at $6707.6$~\AA, which is usually too weak to be
detectable at this age even for high signal-to-noise spectra, is clearly
visible in the spectra of both stars (\figname~\ref{fig:spec2}).
The measured absolute abundances for \bizarreone\ and \sunanalog\ are
$2.75$~dex and $2.25$~dex, respectively (Myles \etal, in prep.),
resulting in the largest abundance difference ($\approx 0.5$~dex) seen
among all measured elements.

@@

Sorting the abundance differences by condensation temperature ($T_C$) of the
elements shows a clear increasing trend.
In \figname~\ref{fig:deltaxh_tcrank},
we show the abundance difference between \bizarreone\ and \sunanalog\ ordered
by each element's equilibrium \Tcondens\ in solar system composition
gas\cite{2003ApJ...591.1220L}.
The five under-enhanced elements in \bizarreone\
relative to \sunanalog\ are the five most volatile of all elements measured.
The differences in \elem{Mn} ($\Tcondens = 1158$~K) and
\elem{Cr} ($\Tcondens = 1296$~K) suggest a break in $\Tcondens \approx 1200$~K.

We interpret the \Tcondens-dependent metal enhancement of \bizarreone\ relative
to \sunanalog\ and the very high surface \elem{Li} abundance ($A(\elem{Li}) =
2.75$) of \bizarreone\ as evidence for accretion of rocky (refractory-rich)
planetary material in \bizarreone.
In a multi-planet system, dynamical instabilities triggered by planet-planet
scattering\cite{TODO} or encounters with a field star\cite{Malmberg:2011aa} can
lead to planet ejection or accretion.
If one of the two stars in a wide binary accreted more refractory-rich (rocky) planets
than the other, this may imprint a strong \Tcondens-dependent
abundance differences like those observed in \bizarreone-\sunanalog.

@@

We estimate that the accretion of $\approx 15$~\mearth\ of rocky planets
in \bizarreone\ relative to \sunanalog\ can explain the enhancement in
refractory elements as well as the surface Li abundance.
Because the anchor star, \sunanalog,
is very similar to the Sun in its stellar properties (\teff, \logg, \feh, age),
we can use assume the Sun's photosphere abundances\cite{Asplund:2009aa} as the
pre-accretion state of \bizarreone.
In \figname~\ref{fig:deltaxh_tcrank}, we show the expected change in solar abundances,
$\Delta\elemH{X}$, after adding $15$~\mearth\ of bulk Earth composition
material\cite{2003TrGeo...2..547M} assuming that 2\% of the star's mass is in
its convective zone\cite{Pinsonneault:2001aa}.
It has long been known that more volatile (low \Tcondens) elements are more
depleted in the Earth relative to CI or other carbonaceous
chondrites\cite{mcdonough2001composition} that are thought to reflect the
elemental composition of the pre-solar nebula. \todo{Check end of last sentence}
This trend is presumed to be closely related to the formation of terrestrial
planets and, in particular to the radial temperature gradient in a
protoplanetary disk.
The trend resulting from adding $15$~\mearth\ of bulk Earth provides an overall
good match to the observed $\Delta\elemH{X}$, suggesting that the
refractory-enhanced star, \bizarreone\, accreted $\approx 15$~\mearth\ more of
rocky planetary material than \sunanalog.

The accretion scenario can naturally explain the anomalously high
surface \elem{Li} abundance in \bizarreone.
Because \elem{Li} is strongly depleted in old sun-like stars, yet
present in bulk Earth with a concentration of $1.1$~ppm\cite{2003TrGeo...2..547M},
late-time accretion of rocky planetary material will significantly
replenish the lithium in the star's surface.
For the present-day Sun, the accretion of $15~\mearth$ of bulk Earth-like
material would result in $\Delta\elemH{Li} \approx 1.6$~dex
(see inset of \figname~\ref{fig:deltaxh_tcrank}).
Incidentally, the \bizarreone-\sunanalog\ system has an age (informed by
stellar parameters) very close to the Sun ($\sim 4$~Gyr).
Thus, as long as we believe the Sun's present-day surface \elem{Li} abundance
to be ordinary, the accretion of $20$~\mearth\ by \bizarreone\ is consistent with a $1.6$~dex
enhancement in \elem{Li} abundance.
This is exactly what we find: the \elem{Li} abundance of \bizarreone\ is
$A(\elem{Li}) = 2.75$ (Table~\ref{tab:t1}, Myles \etal, in prep.)
approximately $1.65$~dex higher than the solar value of $1.05$~dex\cite{Asplund:2009aa}.
Furthermore, this implies that the accretion event should have happened
recently within the \elem{Li} depletion time ($\lesssim 1$~Gyr).

\sunanalog\ is also enhanced in \elem{Li} compared to other stars of similar
ages by $\approx 1$~dex, considering its age of $4.00_{-1.56}^{+1.51}$~Gyr.
This enhancement puts an upper limit on the accreted mass to be
$\approx 4$~\mearth\ assuming a \elem{Li} concentration of $1.1$~ppm
\cite{mcdonough2001composition}, as above.
Unlike \bizarreone, we cannot know the pre-accretion abundances of
\sunanalog.\footnote{
  Strictly speaking, we can never know the pre-accretion abundances
  for \bizarreone\ either.
  We only have an {\it approximate} idea that this is not far from a solar-twin
  star \sunanalog, and because the deviation from this ``anchor'' star is
  large, it is reasonable to consider accretion by the Sun.
  In reality, \sunanalog\ may also have had its own accretion history,
  which indeed seems to be the case according to its \elem{Li} abundance.
}
However, we note that the span of abundance difference between highly volatile
elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}) and refractory elements such
as \elem{Fe} expected from accreting $4$~\mearth\ to the Sun is $\approx
0.05$~dex.
This is comparable to the abundance difference between N, Na, and Fe in
\sunanalog.
It is also interesting that \sunanalog\ shows a deficit in the same volatile
and moderately volatile elements (\elem{C}, \elem{N}, \elem{O}, \elem{Na}, and
\elem{Mn}) relative to Fe as in \bizarreone.
Thus, we conclude that \sunanalog\ is also likely to have had a similar
accretion event, but the amount of accretion was at least 5 times
smaller than \bizarreone.

What triggered the planet engulfment in the two comoving stars
within the last $\sim 1$~Gyr remains unclear.
One possibility is that a fly-by interaction with a field star could have
triggered eccentricity excitation of outer planets around each star, which may
have propagated inward through planet-planet scattering, leading to the accretion of inner rocky planets\cite{Zakamska:2004aa,Malmberg:2011aa}.
If this is the case, there may be surviving, highly-eccentric giant planets.
The two stars have not been included in any publicly released data from planet
search programs, however, outer eccentric planets are potentially detectable with future data releases of the \gaia\ mission.
If both stars have accreted planetary material, it would be very interesting to
search for the existence and architectures of the planetary systems left
behind.

@@

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{deltaxh_tcrank_vari.pdf}
  \caption{Expected differences in solar abundances after adding
    varying mass of bulk Earth material.
    Elements are ordered by their $T_C$ on $x$-axis, same as
    \figname~\ref{fig:deltaxh_tcrank}.
    The solid and dashed lines assume $f_\mathrm{CZ}=0.02$ and $f_\mathrm{CZ} =
    0.03$ respectively.
    For each $f_\mathrm{CZ}$, we show expected $\Delta\elemH{X}$
    for adding 5, 10, 15, 20, 25~\mearth\ of bulk Earth (from bottom to top).
  }
  \label{fig:vari}
\end{figure}

@@

The estimate of accreted mass depends sensitively on $f_\mathrm{CZ}$ and the
mass of the star which are difficult quantities to constrain directly through
data.
While we adopt $(f_\mathrm{CZ},\,M) = (0.02, 1~M_\odot)$, we show the
expected changes in $\Delta\elemH{X}$ for $f_\mathrm{CZ}=0.03$ in
\figname~\ref{fig:vari}.
